acquisition of TEs

### 2021-02-01 Analyze_TEs.Rmd
20210201

mycor <- rcorr(as.matrix(Correlation), type="pearson")
mycor$r
mycor$P

library(corrplot)
mycor <- cor(Correlation) 
corrplot(mycor)
write.csv(mycor, "ObservedTE_correlations.csv", col.names=NA)
```

@@

>>>>

library(Hmisc)
mycor <- rcorr(as.matrix(Correlation), type="pearson")
mycor$r
mycor$P

library(corrplot)
mycor <- round(cor(Correlation), 2)
corrplot(mycor)
write.csv(mycor, "ObservedTE_correlations.csv", col.names=NA)

cor.test(Correlation$TE, Correlation$B, method = "pearson")
cor.test(Correlation$TE, Correlation$W, method = "pearson")
cor.test(Correlation$TE, Correlation$D, method = "pearson")
cor.test(Correlation$TE, Correlation$N, method = "pearson")

@@

##### Facet by W (< 100 vs. > 100)
